Proposal for Analyzing Language Models: Separatablity of Syntax and Semantics

### 2022-04-26 proposal/proposal.tex
minor updates to methods
Removed a sentence in evaluation that incorrectly claimed we would look at train time for the linear classifier. Minor grammatical changes to the rest of the methods section.

We will pair the INLP method with the probing tasks described in sections 2.3 and 2.4 in order to create two guarding functions that will enable us to isolate components of BERT embeddings that syntax-specific and semantics-specific information.

@@

%Description of the data set used and the information it contains relevant to the tasks of interest. Talk about pre-processing the syntax trees to get CCG tags. 
We will use the English V4 subset of the CoNLL 2012 shared task data. We must perform two pre-processing steps for this data to be used for our probing and evaluation tasks. The first is to apply Hockenmaier and Steedman's CCG Derivation algorithm to the parse tree field in the dataset, in order to create the CCG tags for each word. If this proves to be too time-consuming or computationally expensive then we shall change the syntactic probing task to utilize the POS tags available in the dataset in place of CCG tags. The second task is to use the SRL frames in the dataset to generate (verb, BIO-argument-tag) pairs that will act as the categories for the semantic probing task. 
%cite CCG paper

@@

We will assess each of these embedding types and the original BERT embeddings on the CCG and SRL labeling tasks that were used in the probes. We will pay particular attention to accuracy and training time when comparing the various embedding types.

We have also hypothesized several additional assessment tasks that we would like to undertake, if time permits, or relegate to future work. The first of these tasks is to assess how each embedding type performs on the language modeling task. We would also like to perform the evaluation classification task using a feed-forward neural network with a single hidden layer that contains 10 nodes, in order to determine if there is any task-relevant non-linear information present in the embeddings. If time permits, we would also like to look for patterns in the performance of different embeddings, e.g. explore if a particular embedding type tends to perform better/worse on one of the evaluation tasks for words of a particular POS compared to others. Finally, if time permits we would like to repeat the above procedure to explore the embeddings output by different layers of the BERT model. 
%FFNN description is entirely arbitrary, it was just something we talked about during one of our meetings. If anyone has a particular architecture in mind here, please feel free to update this section.

>>>>

We will pair the INLP method with the probing tasks described in sections 2.3 and 2.4 in order to create two guarding functions that will enable us to isolate components of BERT embeddings that contain syntax-specific and semantics-specific information.

@@

%Description of the data set used and the information it contains relevant to the tasks of interest. Talk about pre-processing the syntax trees to get CCG tags. 
We will use the English V4 subset of the CoNLL 2012 shared task data. We must perform two pre-processing steps for this data to be used for our probing and evaluation tasks. The first is to apply Hockenmaier and Steedman's CCG Derivation algorithm to the parse tree field in the dataset, in order to create the CCG tags for each word. If this proves to be too time-consuming or computationally expensive then we shall change the syntactic probing task to utilize the POS tags available in the dataset, in place of CCG tags. The second task is to use the SRL frames in the dataset to generate (verb, BIO-argument-tag) pairs that will act as the categories for the semantic probing task. 
%cite CCG paper

@@

We will assess each of these embedding types and the original BERT embeddings on the CCG and SRL labeling tasks that were used in the probes. We have also hypothesized several additional assessment tasks that we would like to undertake, if time permits, or relegate to future work. The first of these tasks is to assess how each embedding type performs on the language modeling task. We would also like to perform the evaluation classification task using a feed-forward neural network with a single hidden layer that contains 10 nodes, in order to determine if there is any task-relevant non-linear information present in the embeddings. If time permits, we would also like to look for patterns in the performance of different embeddings, e.g. explore if a particular embedding type tends to perform better/worse on one of the evaluation tasks for words of a particular POS compared to others. Finally, if time permits we would like to repeat the above procedure to explore the embeddings output by different layers of the BERT model. 
%FFNN description is entirely arbitrary, it was just something we talked about during one of our meetings. If anyone has a particular architecture in mind here, please feel free to update this section.
